Andres Karjus

### 2021-01-18 index.Rmd
scrollbar

<!-- /*  <style>     </style> */ -->
```{css, echo=FALSE}
.main-container {
max-width:  940px;
min-width: 300px !important;
padding-left: 1px;
}

@@

#TOC {
  text-align: left;
  padding-left: 0px ;
  padding-right: 0px;
  left: 10px;
  top: 0;
  width: 100%;
}
/* the expander thing*/
details summary::-webkit-details-marker {
  display:none;
}

>>>>

<!-- /*  <style>     </style> */ -->
```{css, echo=FALSE}

/* avoids scroll bar jump*/
html { 
  margin-left: calc(100vw - 100%); 
}

.main-container {
max-width:  940px;
min-width: 300px !important;
padding-left: 1px;
}

@@

#TOC {
  text-align: left;
  padding-left: 0px ;
  padding-right: 0px;
  left: 10px;
  top: 0;
  width: 100%;
}

/* the expander thing*/
details summary::-webkit-details-marker {
  display:none;
}
